再生可能なデータ解析入門

### 2019-08-19 how-to-reproducible-analysis.Rmd
update

- renv: [renvの日本語解説資料](https://qiita.com/okiyuki99/items/688a00ca9a58e42e3bfa)

- packrat: [packratの日本語解説資料](https://qiita.com/uri/items/5d473a5df91954585e62)

>>>>

- renv: [okiyuki99氏によるrenvの日本語解説資料](https://qiita.com/okiyuki99/items/688a00ca9a58e42e3bfa)

- packrat: [uri氏によるpackratの日本語解説資料](https://qiita.com/uri/items/5d473a5df91954585e62)
